\chapter{What literature do you recommend for probabilistic databases?}
There is a wide range of literature available on probabilistic databases, covering a variety of topics and perspectives. Some books and papers that I would recommend for learning more about probabilistic databases include:


\begin{itemize}
	\item Probabilistic Databases by Sebastiano Vigna (2013): This book provides a comprehensive introduction to probabilistic databases, covering the foundations of probability theory, the basics of database systems, and the principles and algorithms for probabilistic data management and querying.
	
	\item Probabilistic Graphical Models by Daphne Koller and Nir Friedman (2009): This book provides a detailed introduction to probabilistic graphical models, which are a key tool for representing and reasoning with uncertain or incomplete information in probabilistic databases. The book covers the foundations of probability theory, the principles and algorithms for probabilistic inference, and the applications of probabilistic graphical models in a variety of domains.
	
	\item Probabilistic Relational Models by Ricardo Silva and Joao Gama (2012): This book provides an in-depth introduction to probabilistic relational models, which are a type of probabilistic graphical model that is specifically designed for representing and reasoning with uncertain or incomplete information in relational databases. The book covers the foundations of probability theory, the principles and algorithms for probabilistic inference in relational models, and the applications of probabilistic relational models in a variety of domains.
	
	
	\item Probabilistic Databases: From Theory to Practice by Joseph Y. Halpern, Gerome Miklau, Dan Suciu (2010): This paper provides a survey of the state of the art in probabilistic databases, covering the foundations of probability theory, the principles and algorithms for probabilistic data management and querying, and the applications and challenges of probabilistic databases in practice. The paper also includes a comprehensive bibliography of the literature on probabilistic databases.
	
	

\end{itemize}