\chapter{What other types of databases are there?}

There are many different types of databases, and the type that is best suited to a particular application depends on the specific requirements and constraints of that application. Some common types of databases include:


\begin{enumerate}
	\item Relational databases: These are the most commonly used type of database, and they store data in tables with rows and columns. They use a structured query language (SQL) to access and manipulate the data.
	
	\item Object-oriented databases: These databases are designed to store and manage objects, which are data structures that contain both data and behavior. They are often used in applications that require complex data modeling or real-time data access.
	
	\item NoSQL databases: These databases are designed to store and retrieve data in a more flexible and scalable way than relational databases. They are often used in applications that require high performance, such as social media or gaming platforms.
	
	\item In-memory databases: These databases store data in RAM instead of on disk, which allows for very fast access and manipulation of data. They are often used in applications that require real-time data access, such as financial trading or online gaming.
	
	\item Graph databases: These databases are designed to store and query data that is organized as a network of interconnected nodes and edges. They are often used in applications that require fast analysis of complex relationships, such as social networks or supply chain management.
	
	
	
	
\end{enumerate}