\chapter{What are probabilistic databases used for?}
Probabilistic databases are often used in applications where it is difficult or impossible to obtain complete and accurate data. They can be useful for handling uncertain or incomplete information in a mathematically rigorous way.\\

\vspace{1cm}
Some examples of the types of applications that probabilistic databases are used for include:
\begin{itemize}
	\item Natural language processing: Probabilistic databases can be used to represent the uncertain meanings of words and phrases in natural language text, allowing natural language processing systems to reason about the likely meanings of words and phrases in context.
	
	\item Robotics: Probabilistic databases can be used to represent the uncertain locations of objects in a robot's environment, allowing the robot to reason about the likely locations of objects and plan its actions accordingly.
	
	\item Information extraction: Probabilistic databases can be used to extract structured information from unstructured text, such as extracting dates, locations, and other entities from natural language documents.
	
	\item Recommender systems: Probabilistic databases can be used to represent the preferences and interests of users in a recommendation system, allowing the system to reason about the likely preferences of users and provide personalized recommendations.
\end{itemize}


These are just a few examples of the types of applications that probabilistic databases can be used for. There are many other possible uses for probabilistic databases in a wide variety of domains.
